SciPy 1.0---Fundamental Algorithms for Scientific Computing in Python

### 2019-01-22 scipy-1.0/paper.tex

SciPy's arrival at this point is surprising, and somewhat anomalous.
When started, the library had little funding, and was written mainly
by graduate students---many of them without a computer science education, and often without the
blessing of their advisors.  To even imagine that a small group of
``rogue'' student programmers could upend the already well-established
ecosystem of research software---backed by millions in funding, and
thousands of highly qualified engineers\cite{mathworks-globe-97,
esri-revenue}---was preposterous.

>>>>

SciPy's arrival at this point is surprising, and somewhat anomalous.
When started, the library had little funding, and was written mainly
by graduate students---many of them without a computer science education, and often without the
blessing of their advisors.  To even imagine that a small group of
``rogue'' student programmers could upend the already well-established
ecosystem of research software---backed by millions in funding, and
thousands of highly qualified engineers---was preposterous.
